---
title: "Getting Started with speechmatics"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with speechmatics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

## Authentication

The package uses the Speechmatics API, which requires an API key. Sign up at
<https://www.speechmatics.com/> to get one, then set it as an environment
variable:

```{r}
Sys.setenv(SPEECHMATICS_API_KEY = "your-key-here")
```

For persistent use, add it to your `.Renviron` file:

```
SPEECHMATICS_API_KEY=your-key-here
```

## Basic transcription

`sm_transcribe()` submits an audio file, waits for the result, and writes the
transcript to a text file in your working directory:

```{r}
library(speechmatics)

audio <- system.file("extdata", "testrecording.mp3", package = "speechmatics")
sm_transcribe(audio)
```

You can also specify the output path:

```{r}
sm_transcribe(audio, "my_transcript.txt")
```

## Configuration

Use `sm_transcription_config()` to control language, quality, and diarization:

```{r}
# French, enhanced quality
sm_transcribe(
  audio,
  config = sm_transcription_config(language = "fr", quality = "enhanced")
)
```

### Speaker diarization

Speaker diarization identifies who said what from a single audio channel:

```{r}
sm_transcribe(
  audio,
  config = sm_transcription_config(diarization = sm_diarize_speaker())
)
```

### Channel diarization

Channel diarization separates speakers that are already on different audio
channels:

```{r}
sm_transcribe(
  audio,
  config = sm_transcription_config(
    diarization = sm_diarize_channel(labels = c("Agent", "Caller"))
  )
)
```

## Managing jobs

You can work with jobs directly using the lower-level functions:

```{r}
# list all jobs
jobs <- sm_list_jobs()
jobs

# get a transcript in different formats
sm_get_transcript(jobs$id[1])
sm_get_transcript(jobs$id[1], format = "srt")
sm_get_transcript(jobs$id[1], format = "json-v2")

# delete a job
sm_delete_job(jobs$id[1])
```
